\OurTool{}: Integrative Probing Analysis of Nucleic Acids Empowered by Multiple Accessibility Profiles

### 2020-07-02 IPANEMAP-2019.tex
Updates from Overleaf

\subsection*{\OurTool outperforms state-of-the-art predictive methods when informed by a single profile}
%Mono-probing Mathews (Hadjim)
%* On est meilleur sur la version courante de RSample
%* Multi conformation
We assessed the predictive capacities of \OurTool in a classic setting where a single probing condition is available, and compared its performances against \Software{RSample} software recently introduced by Spacic\etal\cite{Spasic2017}, \Software{RSample} relies on a sampling/clustering method developed independently from the current work. It was shown to perform \RevA{comparably as} a comprehensive collection of state-of-the-art methods in probing-guided structure prediction, including \Software{RME}~\citep{Wu2015}, \Software{RNAprob}~\citep{Deng2016}, \Software{RNAprobing}~\citep{Washietl2012}, \Software{RNAsc}~\citep{Zarringhalam2012} and the \Software{fold} utility from the \Software{RNAStructure} suite~\citep{Reuter2010}.
We considered the Hajdin dataset~\cite{Hajdin2013}, which consists of 24 RNAs of lengths ranging from 47 to 500 nts, all believed to fold into a unique documented conformation.

@@

\RevA{We used the default number of sampled structures for \Software{RSample}, namely 10~000 to compute correction factors and 1~000 for the clustering phase, and \OurTool (1~000 structures).  For all RNAs, a single structure was returned by both software. Note that the Pareto-optimality always implies a single returned cluster/structure for \OurTool{} in a mono probing setting.}
We computed and report in Figure~\ref{fig:Vsrsample} the individual Geometric Means (GM) of predicted structures. \RevA{Sensitivity and PPV can be found in Supp. Table S4, and Supp. Table S5 reports the stability of predictions over 10 independent runs of \OurTool.}

>>>>

\subsection*{\OurTool{} \RevB{performs comparably to} state-of-the-art predictive methods when informed by a single profile}
%Mono-probing Mathews (Hadjim)
%* On est meilleur sur la version courante de RSample
%* Multi conformation
We assessed the predictive capacities of \OurTool in a classic setting where a single probing condition is available, and compared its performances against \Software{RSample} software recently introduced by Spacic\etal\cite{Spasic2017}, \Software{RSample} relies on a sampling/clustering method developed independently from the current work. It was shown to perform \RevA{comparably as} a comprehensive collection of state-of-the-art methods in probing-guided structure prediction, including \Software{RME}~\citep{Wu2015}, \Software{RNAprob}~\citep{Deng2016}, \Software{RNAprobing}~\citep{Washietl2012}, \Software{RNAsc}~\citep{Zarringhalam2012} and the \Software{fold} utility from the \Software{RNAStructure} suite~\citep{Reuter2010}.
We considered the Hajdin dataset~\cite{Hajdin2013}, which consists of 24 RNAs of lengths ranging from 47 to 500 nts, all believed to fold into a unique documented conformation.

@@

\RevA{We used the default numbers of sampled structures for \Software{RSample} and \OurTool{}, namely 10~000 to compute correction factors and 1~000 for the clustering phase.  For all RNAs, a single structure was returned by both software. Note that the Pareto-optimality always implies a single returned cluster/structure for \OurTool{} in a mono probing setting.}
We computed and report in Figure~\ref{fig:Vsrsample} the individual Geometric Means (GM) of predicted structures. \RevA{Sensitivity and PPV can be found in Supp. Table S4, while Supp. Table S5 reports the stability of predictions over 10 independent runs of \OurTool.}

\RevB{%
\OurTool{} appears to perform comparably, or even slightly favorably, to \Software{RSample}, reporting more accurate structures than its competitor for roughly two thirds of the tested RNAs, while averaging $80.1\%$ GM. However, the  improvement is only of around 1.5\% on average over the \citet{Hajdin2013} dataset, an improvement that is no longer significant according to a two-tailed paired T-test.
}
